\vspace*{0.75in}
\begin{center} {\bf Declaration}\end{center}

%The research results presented in this thesis are the product of my own work. Appropriate references are provided when results of third parties are mentioned. The research presented here was not submitted for another degree in any other department or university.

The research results presented in this thesis are the product of my own work unless otherwise stated. Appropriate references are provided when results of third parties are mentioned. 

Chapters 1 and 2 are reviews of neutrino physics with descriptions of the current theory and experimental results. The review was carried out by the author with references to established literature and articles produced by experiments. Chapter 3 contains a description of the Baby MIND and WAGASCI detectors. This contains results from the Baby MIND and WAGASCI collaborations together and much has been developed by numerous collaborators. Much of the work with the design and both scintillators and magnets was started before I joined the Baby MIND collaboration, however I was heavily involved in the construction, validation and test beam. Details regarding the construction and test beam were presented by the author at the NuPhys2016~\cite{51Saba, 54NUFACT2016Hallsjo} and NuFact17~\cite{82Uppsala} conferences. The WAGASCI detector was fully developed before I joined the WAGASCI detector and all work has been referenced to the appropriate colleagues. The simulation software described in chapter 4 was already developed to some degree at the group at the University of Glasgow. This software was further developed to provide a framework which could be used for the Baby MIND collaboration. The main part of my work in the collaboration was to lead the simulation and reconstruction efforts using a heavily modified version of this initial software. The specific functionality that was added and maintained have been described and was in part presented presented by the author at NuFact17~\cite{82Uppsala}. Over the course of this thesis a new framework was developed which is all of my own work. In chapter 5 the test beam studies are described. I was part of the data taking and software development, however much of the credit of the hardware results and the specifics of the data taking goes to my collaborators. The data analysis and usage of the reconstruction software was my own work. The test beam data were collected in the summer of 2016 and 2017 and presented at NuFact17~\cite{82Uppsala}. Chapter 6 and 7 present NuSTORM and J-PARC beam studies on neutrino interactions. The various neutrino spectra and data taking from J-PARC was provided by the collaboration however the studies are entirely my own work. The data was collected between March and May 2018 and was in part presented by the author at NuFact18.

The research presented here was not submitted for another degree in any other department or university.


\begin{flushright} \textbf{Sven-Patrik Philip George Hallsj{\"o}}\end{flushright}
