\chapter{Neutrino interaction studies}
\label{c:neutrino}

Lab report again, trying to estimate cross-section of interactions. Why? Need it to improve oscillation measurements. Using simulations of muon neutrinos from simulation. What is done, what cuts? How Do we calculate cross-sections? Angular acceptance, look at what Marc has done, do similar things and further the calculations.

Discuss what to expect, what kind of interactions could happen in the TASD/WAGASCI? What could be seen? What information? Baby MIND can also have interactions, which ones would be visible? Can reconstruct muons in Baby MIND, electrons and pions visible and potentially reconstructable, but not now.


Charge id, momentum. Identifying muons comming of the neutrino interaction with a specific beam and interaction area.

Describe the fiducial volume like in my talk for NuFACT.

\section{Muon charge current quasi-elastic}

Direct simulations with CCQE and different geometries. Use data from specifically Baby MIND in B2 beam line. Explain the beam line etc etc.

CCQE from muon neutrino produces a muon. Clear production and easy to identify in TASD, not possible in MIND due to the design. 



Acceptance study, detector layout. Beam settings? Add charge reconstruction, momentum reconstruction. Particle ID? also need interaction ID from TMVA.

Different size gap, different detector layout both early/testbeam and new at Japan.


Cross-section studies. Look at what Marc has done! 

Discuss with paul what and how to do cross-section measurements.

\subsection{Interactions in TASD+ Baby MIND}
Simulations for a nustorm like beam, explain the details and event selection.

Interaction in TASD, use as a filter for CCQE but not as part of the analysis. Shown at NuSTORM talk, fix momentum slightly.

\subsection{Neutrino interactions in Iron in Baby MIND}
Simulations for a  T2K like beam, explain the details and event selection, (None for simulation but easy enough with data). Use the specific fiducial volume.

\subsubsection{Simulations vs data}
Show same as for nuFact, explain in detail what was done. Show the data.


\section{Future studies}

\subsection{Neutrino interactions in WAGASCI + Baby MIND}

Using WAGASCI as a CCQE identification,

\subsubsection{Interactions in the full WAGASCI}

Discuss future data taking, interactions everywhere etc etc.

%\subsection{GAr + BabyMIND}
%\subsubsection{Analysis Simulations}
%\subsection{TASD + BabyMIND}
%\subsubsection{Analysis Simulations}
%\subsection{Full WAGASCI}
%\subsubsection{Analysis with Simulations}
%\subsubsection{Simulations vs data}

%\section{Electron charge current quasi-elastic}

